Fitting Synchrotron Models to Gamma-Ray Burst Data from INTEGRAL/SPI

### 2021-12-17 src/ms.tex
asd

All the fits in this section are done with 3ML \3ML and the Bayesian sampling algorithm MultiNest \multinest to create full posterior distributions of the parameters. To visualize the posterior distribution we use ChainConsumer \chainconsumer with the output from MultiNest to create corner plots.

>>>>

All the fits in this section are done with 3ML and the Bayesian sampling algorithm MultiNest to create full posterior distributions of the parameters. To visualize the posterior distribution we use ChainConsumer with the output from MultiNest to create corner plots.
